TODO

### 2015-06-02 ccs.tex
Update author and paper metadata and turn on page numbering
Further work on the introduction

\documentclass{sig-alternate}

@@

\begin{document}
%
% --- Author Metadata here ---
\conferenceinfo{CCS}{2015 Denver, Colorado, USA}
%\CopyrightYear{2015} % Allows default copyright year (20XX) to be over-ridden - IF NEED BE.
%\crdata{0-12345-67-8/90/01}  % Allows default copyright data (0-89791-88-6/97/05) to be over-ridden - IF NEED BE.
% --- End of Author Metadata ---

@@

\numberofauthors{3}
\author{
Daniel~R.~Thomas
\and
Alastair~R.~Beresford\\
       \affaddr{Computer Laboratory}\\
       \affaddr{University of Cambridge}\\
       \affaddr{Cambridge, United Kingdom}\\
       \email{Firstname.Lastname@cl.cam.ac.uk}
\and
Andrew~Rice
}

@@

By producing a scoring metric which compares different entities such as device manufacturers or network operators or specific device models we can provide information which allows device purchasers to select devices with better security.
We know that organisations want to buy devices with better security and which receive updates, for example the CESG which advises UK government a advocates this~\cite{CESG2013} and we are collaborating with a FTSE 100 company to give them better information.
Before we provided this information in this paper it was not available.
We provide the answer to the question ``Who should I buy my Android phone from for best security?''

@@

\begin{figure}
\centering
\includegraphics[width=\columnwidth]{figures/proportioninsecure}
\caption{Proportion of devices running insecure, maybe secure and secure versions of Android against time.
The red vertical lines are caused by vulnerabilities being discovered with those which have the biggest impact annotated.
}
\label{fig:proportioninsecure}
\end{figure}

It is clear from Figure~\ref{fig:proportioninsecure} that Android devices are often exposed to known security vulnerabilities.
One solution is regulation, and indeed there is ongoing legal action to force network operators to ship updates for security vulnerabilities~\cite{Soghoian2013}.\todolater{Check on the status of this legal action}
Many smartphones are sold on 12--24 month contracts, and yet our data shows many devices do not receive many security updates, with an overall average of \daUpdatesPerYearNominal\ per year. 
In contrast, Windows XP could be purchased for a one-off payment in October 2001 and received security updates until April 2014.

An alternative to regulation is access to publicly available data. 
Comparative data would provide an incentive to both device manufacturers and network operators to provide updates.
Currently corporate and public sector buyers are encouraged to purchase secure devices, but we have found little concrete guidance on the specific makes and models providing the best security. 
For example, CESG, which advises the UK government on how to secure its computer systems, recommends picking Android device models from device manufactures which are good at shipping security updates promptly~\cite{CESG2013} but it does not state which device manufacturers these are.
To address this, we developed a scoring system and provide numbers on the historic performance of device models in the \da\ project in~\S\ref{sec:security_scoring}.

In summary, the contributions of this paper are:
\begin{itemize}
 \item We measure the security of Android according to three metrics and compare different device manufacturers and device models to allow device purchasers to differentiate between them based on security.
\end{itemize}

>>>>

\documentclass{sig-alternate}
\pagenumbering{arabic}

@@

\begin{document}
%
% --- Author Metadata here ---
\conferenceinfo{SPSM}{2015 Denver, Colorado, USA}
%\CopyrightYear{2015} % Allows default copyright year (20XX) to be over-ridden - IF NEED BE.
%\crdata{0-12345-67-8/90/01}  % Allows default copyright data (0-89791-88-6/97/05) to be over-ridden - IF NEED BE.
% --- End of Author Metadata ---

@@

\numberofauthors{3}
\author{
\href{http://orcid.org/0000-0001-8936-0683}{Daniel~R.~Thomas}
\and
Alastair~R.~Beresford\\
       \affaddr{Computer Laboratory}\\
       \affaddr{University of Cambridge}\\
       \affaddr{Cambridge, United Kingdom}\\
       \email{Firstname.Lastname@cl.cam.ac.uk}
\and
Andrew~Rice
}

@@

By producing a scoring metric which compares different entities such as device manufacturers or network operators or specific device models we can provide information which allows device purchasers to select devices with better security.
Currently corporate and public sector buyers are encouraged to purchase secure devices, but we have found little concrete guidance on the specific makes and models providing the best security.
For example, CESG, which advises the UK government on how to secure its computer systems, recommends picking Android device models from device manufactures which are good at shipping security updates promptly~\cite{CESG2013} but it does not state which device manufacturers these are.
We are also collaborating with a FTSE 100 company to give them concrete information.
To address this, we developed a scoring system and provide numbers on the historic performance of device models in the \da\ project in~\S\ref{sec:security_scoring}.
We provide the answer to the question ``Who should I buy my Android phone from for best security?'', in general Nexus devices are better, further details are given in \S\ref{sec:security_scoring}.

@@

\begin{figure}
\centering
\includegraphics[width=\columnwidth]{figures/proportioninsecure}
\caption{Proportion of devices running insecure, maybe secure and secure versions of Android against time.
The red vertical lines are caused by vulnerabilities being discovered with those which have the biggest impact annotated.
}
\label{fig:proportioninsecure}
\end{figure}
By using data from \da~\cite{Wagner2013} we can examine the versions of Android running on user devices over time and through comparison with data on which versions of Android were vulnerable to different critical vulnerabilities~\cite{androidvulnerabilities.org} we can plot the exposure of Android devices to known critical vulnerabilities.
Figure~\ref{fig:proportioninsecure} shows that Android devices are often exposed to known security vulnerabilities.
One solution to this problem is regulation, and indeed there is ongoing legal action to force network operators to ship updates for security vulnerabilities~\cite{Soghoian2013}.\todolater{Check on the status of this legal action}
Many smartphones are sold on 12--24 month contracts, and yet our data shows many devices do not receive many security updates, with an overall average of \daUpdatesPerYearNominal\ per year. 
In contrast, Windows XP could be purchased for a one-off payment in October 2001 and received security updates until April 2014.
An alternative to regulation is access to publicly available data, which we provide in this paper.
Comparative data would provide an incentive to both device manufacturers and network operators to provide updates.

\todo{continue here}
In summary, the contributions of this paper are:
\begin{itemize}
 \item We measure the security of Android according to three metrics and compare different device manufacturers and device models to allow device purchasers to differentiate between them based on security.
\end{itemize}
